% Bibliography — IEEE-style numbered references (reference group format)
\newpage
\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}
\thispagestyle{plain}

\noindent [1] Vercel Inc., ``Next.js Documentation,'' 2024. [Online]. Available: \url{https://nextjs.org/docs}. [Accessed: Apr. 7, 2026].

\vspace{0.3cm}

\noindent [2] Prisma Data Inc., ``Prisma ORM Documentation,'' 2024. [Online]. Available: \url{https://www.prisma.io/docs}. [Accessed: Apr. 7, 2026].

\vspace{0.3cm}

\noindent [3] Mozilla Developer Network, ``Progressive Web Apps,'' 2024. [Online]. Available: \url{https://developer.mozilla.org/en-US/docs/Web/Progressive_web_apps}. [Accessed: Apr. 7, 2026].

\vspace{0.3cm}

\noindent [4] ISO/IEC 18004:2015, ``Information technology---Automatic identification and data capture techniques---QR Code bar code symbology specification,'' International Organization for Standardization, 2015.

\vspace{0.3cm}

\noindent [5] Object Management Group, ``Unified Modeling Language Specification, Version 2.5.1,'' OMG Document formal/2017-12-05, Dec. 2017.

\vspace{0.3cm}

\noindent [6] R.~J. Hyndman and G. Athanasopoulos, \textit{Forecasting: Principles and Practice}, 3rd ed. Melbourne, Australia: OTexts, 2021. [Online]. Available: \url{https://otexts.com/fpp3/}

\vspace{0.3cm}

\noindent [7] Dr.~Babasaheb Ambedkar Technological University, Lonere, ``Department of Computer Engineering---B.Tech Project Report Format Guidelines,'' Raigad, Maharashtra, India, 2025.

\vspace{0.3cm}

\noindent [8] M. Jones, J. Bradley, and N. Sakimura, ``JSON Web Token (JWT),'' RFC 7519, Internet Engineering Task Force (IETF), May 2015. [Online]. Available: \url{https://www.rfc-editor.org/rfc/rfc7519}
