\chapter{Software Requirement Analysis}

\section{Introduction}
This chapter defines the problem in operational terms, identifies stakeholders, and specifies functional and non-functional requirements. Modules are decomposed with responsibilities suitable for implementation in Next.js API routes and React components.

\section{Problem Definition}
The canteen operates with finite ready-to-eat stock. Students should complete ordering and payment before reaching the counter, presenting only a token/QR for pickup. The system must never confirm payment for items that exceed app-tracked stock at payment time. Staff must update stock when physical count differs from the database (e.g.\ exactly 17 samosas remaining) because cash sales are not automatically recorded.

\section{Stakeholders}
\begin{itemize}
  \item \textbf{Student:} Browses menu, pays online, monitors order status, displays QR at pickup.
  \item \textbf{Canteen staff:} Monitors queue, prepares food, verifies pickup, updates inventory.
  \item \textbf{Project guide / examiner:} Evaluates completeness, documentation, and demonstration.
  \item \textbf{College IT (future):} May host HTTPS deployment and database backups.
\end{itemize}

\section{Assumptions and Constraints}
\begin{itemize}
  \item One canteen outlet; single menu list.
  \item Simulated payment acceptable for academic demonstration.
  \item Staff have smartphones with camera for QR scanning.
  \item Internet available on campus Wi-Fi or mobile data.
  \item English UI; currency in Indian Rupees (\inr).
\end{itemize}

\section{Functional Requirements}

\subsection{FR1 -- Authentication}
\begin{itemize}
  \item FR1.1: User shall register with email, name, and optional student ID.
  \item FR1.2: User shall login with email and password.
  \item FR1.3: System shall assign role STUDENT or STAFF and enforce route access.
  \item FR1.4: Session shall persist using secure HTTP-only cookie (JWT).
\end{itemize}

\subsection{FR2 -- Student Menu and Cart}
\begin{itemize}
  \item FR2.1: Display menu with emoji, price, description, category filter.
  \item FR2.2: Show availability: Available, Only N left, Sold out.
  \item FR2.3: Highlight today's special item.
  \item FR2.4: Cart quantity shall not exceed \texttt{stockQuantity}.
  \item FR2.5: Reorder last paid order when items still available.
\end{itemize}

\subsection{FR3 -- Order and Payment}
\begin{itemize}
  \item FR3.1: Validate cart stock via API before review step.
  \item FR3.2: Create order in PENDING state with line items.
  \item FR3.3: Process simulated payment; on success set CONFIRMED and deduct stock.
  \item FR3.4: Generate unique \texttt{orderCode}, \texttt{tokenNumber}, and QR image.
\end{itemize}

\subsection{FR4 -- Pickup and Staff}
\begin{itemize}
  \item FR4.1: List paid orders in staff queue with polling refresh.
  \item FR4.2: Staff marks CONFIRMED $\rightarrow$ READY\_FOR\_PICKUP.
  \item FR4.3: Verify by QR scan or manual token/order code entry.
  \item FR4.4: Confirm handover $\rightarrow$ COMPLETED.
\end{itemize}

\subsection{FR5 -- Inventory}
\begin{itemize}
  \item FR5.1: Staff sets exact \texttt{stockQuantity} (custom count).
  \item FR5.2: Staff adds quantity to existing stock (\texttt{addStock}).
  \item FR5.3: Staff toggles \texttt{isAvailable} for sold-out online.
\end{itemize}

\subsection{FR6 -- Forecast}
\begin{itemize}
  \item FR6.1: Display predicted demand per item and suggested batch size.
  \item FR6.2: Show disclaimer when historical data is limited.
\end{itemize}

\section{Non-Functional Requirements}
\begin{table}[htbp]
  \centering
  \caption{Non-functional requirements}
  \tablebodysetup
  \begin{tabularx}{\textwidth}{@{}l l Y@{}}
    \toprule
    \textbf{ID} & \textbf{Category} & \textbf{Specification} \\
    \midrule
    NFR1 & Usability & Mobile-first; bottom navigation; min.\ touch target 44px \\
    NFR2 & Performance & Menu API cache 8s; poll only when tab visible \\
    NFR3 & Reliability & Stock checks at cart, order, payment \\
    NFR4 & Security & bcrypt passwords; staff-only inventory APIs \\
    NFR5 & Compatibility & Chrome Android, Safari iOS, responsive CSS \\
    NFR6 & Maintainability & TypeScript, modular components, Prisma schema \\
    \bottomrule
  \end{tabularx}
\end{table}

\section{Module Decomposition}
\begin{table}[htbp]
  \centering
  \caption{Modules and functionalities}
  \tablebodysetup
  \begin{tabularx}{\textwidth}{@{}>{\bfseries}p{0.22\textwidth} Y@{}}
    \toprule
    \textbf{Module} & \textbf{Responsibilities} \\
    \midrule
    AuthModule & Login, register, JWT session, role guard \\
    MenuModule & Fetch items, enrich stock labels, daily special \\
    CartModule & Client cart state, validate against server \\
    OrderModule & Create order, status transitions, history \\
    PaymentModule & Simulated pay, stock deduction, token issue \\
    ReceiptModule & QR generation, fullscreen display, polling \\
    QueueModule & Staff list, mark ready, visibility polling \\
    VerifyModule & Parse QR, match order, handover confirm \\
    InventoryModule & PATCH stock, availability toggle \\
    ForecastModule & Aggregate history, weighted average \\
    PWAModule & Manifest, service worker, install UI hints \\
    \bottomrule
  \end{tabularx}
\end{table}

\section{Order Status Rules}
Paid orders progress: \texttt{CONFIRMED} (paid, preparing) $\rightarrow$ \texttt{READY\_FOR\_PICKUP} $\rightarrow$ \texttt{COMPLETED} after verification and handover. \texttt{PENDING} exists only before payment. \texttt{CANCELLED} is reserved for future refund workflows.
